Preliminary Thesis Defence

### 2014-02-26 presentationPTD.tex
update presentation

\usepackage[english]{babel}
%\usepackage[utf8]{inputenc}
%\usepackage{times}
%\usepackage[T1]{fontenc}
\usepackage[authordate,noibid,backend=biber]{biblatex-chicago}
\usepackage[]{hyperref}

@@

\title[]{Preliminary Thesis Defence}
\subtitle{December 18, 2013}

@@

\begin{frame}{Questions}
Cryptocurrency Inflation
	\begin{itemize}
		\item Relevant enough for Development Economics?
	\end{itemize}
Knightian Uncertainty:
	\begin{itemize}
		\item What to do with this critique?
	\end{itemize}
Pensions and  Child Growth:
	\begin{itemize}
		\item Defining of Age-Based and Height-Based Z-scores,\\ correct?
		\item BMI as convex mapping of Weight-for-Height,\\ significance?
		\item Drop in children living with recipient 2008-2012,\\ 		how to account for this?
	\end{itemize}
\end{frame}

@@

\begin{frame}{Uncertainty and Risk in Currency Attacks}{Knightian Uncertainty in Morris and Shin (1998)}
A review of \citetitle{morris1998unique} \parencite{morris1998unique}
\begin{itemize}
	\item Based on currency models \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models}
	\item Finds a unique equilibrium when `uncertainy' is added
\end{itemize}
Critiques:
\begin{itemize}
	\item Strange result, does not correspond to reality
	\item The `distortion' changes uncertainty to risk, effectively increasing the body of knowledge
	\item The distortion of perception has a uniform distribution, results do not hold under e.g. Gaussian
	\item Speculator risk profile is redefined:
\end{itemize}
\begin{quotation}
	For the next step,
	consider the strategy profile where every speculator attacks the currency if and only if
	the message $x$ is less than some fixed number $k$.
	\hspace{\stretch{1}}\parencite[p.~592]{morris1998unique}
\end{quotation}
\end{frame}

@@

\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa I}
	\begin{itemize}
		\item Based on \citetitle{duflo2003grandmothers} \parencite{duflo2000child,duflo2003grandmothers} methodology
		\item Address the issue of eligibility-age discrepancy
		\item South African Household Survey \parencite{saldru2008nids,saldru2012nids,saldru2013nids}
		\item Elibility-age equalisation in 2009
	\end{itemize}
	Model:
	\setcounter{equation}{2}
	\begin{equation}
		\label{sa:eq:interaction}
		y_{it} = \gamma_i + \lambda_t + \mu P^f_{it} + \nu P^m_{it} + X_{it} + \delta T_{it} + \rho T_{it}*P^m_{it} + \epsilon_{it}
		\end{equation}
\end{frame}

\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa II}
	\begin{table}[!ht]
	\centering
	\caption{Height-for-Age Z-score}
	\label{sa:ta:haz}
		\begin{tabular}{l|rrr}
		\hline
		specification & 1 & 2 & 3\\
		\hline
		w\_spen\_m & 0.2366 & *0.8228 & 0.7908 \\
		w\_spen\_w & -0.2331 & 0.1053 & 0.1072 \\
		elig.men.60 & & **-0.3419 & **-0.3465 \\
		w\_spen\_m1:elig.men.60 & & & 0.0446 \\
		w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
		\end{tabular}
	\end{table}
\end{frame}

\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa III}
	\begin{table}[!ht]
	\centering
	\caption{Weight-for-Age Z-score}
	\label{sa:ta:waz}
	\begin{tabular}{l|rrr}
		\hline
		specification & 1 & 2 & 3\\
		\hline
		w\_spen\_m & 0.2366 & 0.2981 & 0.4780 \\
		w\_spen\_w & -0.2331 & -0.3112 & -0.3280 \\
		elig.men.60 & & ***-0.3475 & **-0.3243 \\
		w\_spen\_m1:elig.men.60 & & & -0.2545 \\
		w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
		\end{tabular}
	\end{table}
\end{frame}

\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa IV}
% LaTeX table created manually
% Fri Dec 27 23:53 2013
\begin{table}[!ht]
\centering
\caption{Weight-for-Height Z-score}
\label{sa:ta:whz}
\begin{tabular}{l|rrr}
\hline
specification & 1 & 2 & 3 \\
\hline
w\_spen\_m &  -0.3532 & -0.3210 & -0.4303 \\
w\_spen\_w & 0.0655 & 0.0371 & 0.0478 \\
elig.men.60 & & -0.1417 & -0.1574 \\
w\_spen\_m1:elig.men.60 & & & 0.1484 \\
\end{tabular}
\end{table}
\begin{table}[!ht]
\centering
\caption{Body-Mass-Index Z-score}
\label{sa:ta:bmiz}
\begin{tabular}{l|rrr}
\hline
specification & 1 & 2 & 3 \\
\hline
w\_spen\_m & *-0.8058 & *-0.7905 & *-1.0226 \\
w\_spen\_w & -0.1592 & -0.1956 & -0.1742 \\
elig.men.60 & & -0.1674 & -0.2049 \\
w\_spen\_m1:elig.men.60 & & & 0.3407 \\
\end{tabular}
\end{table}
\end{frame}

@@

Questions  
	\begin{itemize}
	\item
		Cryptocurrency Inflation: relevant for Development Economics?
	\item
		Knightian Uncertainty: What to do with this critique?
	\item
		Pensions and  Child Growth: Account for drop in no. children?
	\end{itemize}
\end{frame}

>>>>

\usepackage[english]{babel}
\usepackage{mathtools}
\usepackage{accents}
%\usepackage[utf8]{inputenc}
%\usepackage{times}
%\usepackage[T1]{fontenc}
\usepackage[authordate,noibid,backend=biber]{biblatex-chicago}
\usepackage[]{hyperref}

@@

\title[]{Preliminary Thesis Defence}
\subtitle{\today}

@@

\begin{frame}{Questions}
Cryptocurrency Inflation
	\begin{itemize}
		\item Relevant enough for Development Economics?
	\end{itemize}
Knightian Uncertainty:
	\begin{itemize}
		\item What to do with this critique?
	\end{itemize}
Pensions and  Child Growth:
	\begin{itemize}
		\item Negative policy effect \\ explanation?
		\item Defining of Age-Based and Height-Based Z-scores,\\ correct?
		\item BMI as convex mapping of Weight-for-Height,\\ significance?
	\end{itemize}
\end{frame}

@@

\begin{frame}{Uncertainty and Risk in Currency Attacks}{Knightian Uncertainty in Morris and Shin (1998)}
A review of \citetitle{morris1998unique} \parencite{morris1998unique}
	\begin{itemize}
		\item Based on currency models \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models}
		\item Finds a unique equilibrium when `uncertainy' is added
	\end{itemize}
	Model:
	\begin{itemize}
		\item State of economic fundamentals: $\theta \sim U[0,1]$
		\item Pegged at a level larger than fundamentals: ($e* \geq f(\theta)$)
		\item Speculators can short, their payoff: $e^* - f(\theta) - t$
		\item Peg cost: economic fund. and speculators attacking ($\alpha$)
		\item Government derives value: $\nu - c(\alpha, \theta)$ from defending peg
	\end{itemize}
	Outcomes:
	\begin{enumerate}
		\item $ [0, \underaccent{\bar}{\theta} ] $, cost always too high, unstable region
		\item $[\underaccent{\bar}{\theta}, \bar{\theta}]$, enough attack, cost too high, `ripe for attack'
		\item $[\bar{\theta}, 1]$, cost of shorting always outweigh gains, stable region
	\end{enumerate}
\end{frame}

\begin{frame}{Uncertainty and Risk in Currency Attacks}
	Critiques:
	\begin{enumerate}

		\item Strange result, does not correspond to reality
		\item The `distortion' changes uncertainty to risk, effectively increasing the body of knowledge
		\item The distortion of perception has a uniform distribution, results do not hold under e.g. Gaussian
		\item Speculator risk profile is redefined:
	\end{enumerate}
	\begin{quotation}
		For the next step,
		consider the strategy profile where every speculator attacks the currency if and only if
		the message $x$ is less than some fixed number $k$.
		\hspace{\stretch{1}}\parencite[p.~592]{morris1998unique}
	\end{quotation}
\end{frame}

@@

\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa}
	\begin{itemize}
		\item Based on \citetitle{duflo2003grandmothers} \parencite{duflo2000child,duflo2003grandmothers} methodology
		\item Address the issue of eligibility-age discrepancy
		\item South African Household Survey \parencite{saldru2008nids,saldru2012nids,saldru2013nids}
		\item Elibility-age equalisation in 2009
	\end{itemize}
	Model:
	\setcounter{equation}{2}
	\begin{equation}
		\label{sa:eq:interaction}
		y_{it} = \gamma_i + \lambda_t + \mu P^f_{it} + \nu P^m_{it} + X_{it} + \delta T_{it} + \rho T_{it}*P^m_{it} + \epsilon_{it}
		\end{equation}
\end{frame}

\begin{frame}{Pensions and Child Growth}{Results: Age-Based Z-scores}
	\begin{table}[!ht]
	\centering
	\caption{Height-for-Age Z-score}
	\label{sa:ta:haz}
		\begin{tabular}{l|rrr}
		\hline
		specification & 1 & 2 & 3\\
		\hline
		w\_spen\_m & 0.2366 & *0.8228 & 0.7908 \\
		w\_spen\_w & -0.2331 & 0.1053 & 0.1072 \\
		elig.men.60 & & **-0.3419 & **-0.3465 \\
		w\_spen\_m1:elig.men.60 & & & 0.0446 \\
		\end{tabular}
	\end{table}
	\begin{table}[!ht]
	\centering
	\caption{Weight-for-Age Z-score}
	\label{sa:ta:waz}
	\begin{tabular}{l|rrr}
		\hline
		specification & 1 & 2 & 3\\
		\hline
		w\_spen\_m & 0.2366 & 0.2981 & 0.4780 \\
		w\_spen\_w & -0.2331 & -0.3112 & -0.3280 \\
		elig.men.60 & & ***-0.3475 & **-0.3243 \\
		w\_spen\_m1:elig.men.60 & & & -0.2545 \\
		\end{tabular}
	\end{table}	
\end{frame}

\begin{frame}{Pensions and Child Growth}{Results: Height-Based Z-scores}
% LaTeX table created manually
% Fri Dec 27 23:53 2013
\begin{table}[!ht]
\centering
\caption{Weight-for-Height Z-score}
\label{sa:ta:whz}
\begin{tabular}{l|rrr}
\hline
specification & 1 & 2 & 3 \\
\hline
w\_spen\_m &  -0.3532 & -0.3210 & -0.4303 \\
w\_spen\_w & 0.0655 & 0.0371 & 0.0478 \\
elig.men.60 & & -0.1417 & -0.1574 \\
w\_spen\_m1:elig.men.60 & & & 0.1484 \\
\end{tabular}
\end{table}
\begin{table}[!ht]
\centering
\caption{Body-Mass-Index Z-score}
\label{sa:ta:bmiz}
\begin{tabular}{l|rrr}
\hline
specification & 1 & 2 & 3 \\
\hline
w\_spen\_m & *-0.8058 & *-0.7905 & *-1.0226 \\
w\_spen\_w & -0.1592 & -0.1956 & -0.1742 \\
elig.men.60 & & -0.1674 & -0.2049 \\
w\_spen\_m1:elig.men.60 & & & 0.3407 \\
\end{tabular}
\end{table}
\end{frame}

@@

Questions  
	\begin{itemize}
	\item
		Negative policy effect: explanation?
	\item
		Cryptocurrency Inflation: relevant for Development Economics?
	\item
		Knightian Uncertainty: What to do with this critique?
	\end{itemize}
\end{frame}
